COVID Shutdown Regulations Negatively Impact Employment and Sales of Restaurants in Ontario

### 2021-02-25 outputs/paper/paper.Rmd
Commit for survey screenshots

---
title: "COVID Shutdown Regulations Negatively Impact Employment and Sales of Restaurants in Ontario"
author: "Hong Shi, Hong Pan, Yixin Guan, Babak Mokri"
thanks: "Code and data are available at: https://github.com/honn-ishinn/restaurants_covid_shutdown"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Due to the world-wide COVID-19 pandemic, shutdown restrictions on businesses and facilities have limited economic activities into a recession. This paper examines the shutdown effect on restaurants by reopening a city in Ontario (Peterborough) and comparing its restaurant operating situation with that of another city (Brantford) after three months reopening. The survey result indicates that shutdown restrictions have negative impacts on restaurant employment, sales and future operation. However, the higher increased COVID cases in the reopened city sugguests the Ontario government to mindfully plan for futher policy decisions."
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
toc: FALSE
bibliography: references.bib

@@

# Appendix {-}

>>>>

---
title: "COVID Shutdown Regulations Negatively Impact Employment and Sales of Restaurants in Ontario"
author: "Hong Shi, Hong Pan, Yixin Guan, Babak Mokri"
thanks: "Code and data are available at: https://github.com/honn-ishinn/restaurants_covid_shutdown"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Due to the world-wide COVID-19 pandemic, shutdown restrictions on businesses and facilities have limited economic activities into a recession. This paper examines the shutdown effect on restaurants by reopening a city in Ontario (Peterborough) and comparing its restaurant operating situation with that of another city (Brantford) after three months reopening. The survey result indicates that shutdown restrictions have negative impacts on restaurant employment, sales and future operation. However, the higher increased COVID cases in the reopened city sugguests the Ontario government to mindfully plan for futher policy decisions."
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
toc: FALSE

header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}

bibliography: references.bib

@@

# Appendix A

Link to access the first survey about restaurant business conditions conducted in September, 2020:
https://docs.google.com/forms/d/1Bl8CbJiN8sUbhsDdnzqP4ifIyE9KT8iJgYI9ldcR2g8

```{r survey1s, echo=FALSE,fig.align='center',fig.cap="Scripts to contact with restaurant owners in the first survey", out.width = '80%'}
# Referenced this link to include image in R markdown
# https://stackoverflow.com/questions/25166624/insert-picture-table-in-r-markdown
knitr::include_graphics(here("outputs/images/survey1_script.png"))
```

```{r survey1c, echo=FALSE,fig.align='center',fig.cap="Consent form of the first survey", out.width = '80%'}
knitr::include_graphics(here("outputs/images/survey1_script.png"))
```

```{r survey1q, echo=FALSE, fig.align='center', fig.cap="Survey questions in the first survey", out.width = '80%'}
knitr::include_graphics(here("outputs/images/survey1_question.png"))
```
```{r survey1t, echo=FALSE, fig.align='center', fig.cap="Thanks section of the first survey", out.width = '80%'}
knitr::include_graphics(here("outputs/images/survey1_thanks.png"))
```

# Appendix B

Link to access the second survey about impact of COVID-19 on restaurants conducted in January, 2021:
https://docs.google.com/forms/d/1FXSeKFkvCtM41k9xFYjQQ_eDGdBs9skVYZ3zU5LNRgY

```{r survey2s, echo=FALSE, fig.align='center', fig.cap="Scripts to contact with restaurant owners in the second survey", out.width = '80%'}
knitr::include_graphics(here("outputs/images/survey2_script.png"))
```

```{r survey2c, echo=FALSE,fig.align='center',fig.cap="Consent form of the second survey", out.width = '80%'}
knitr::include_graphics(here("outputs/images/survey2_consent.png"))
```

```{r survey2q1toq4, echo=FALSE,fig.align='center',fig.cap="Survey questions 1 - 4 in the second survey", out.width = '60%'}
knitr::include_graphics(here("outputs/images/survey2_q1q4.png"))
```

```{r survey2q5toq8, echo=FALSE,fig.align='center',fig.cap="Survey questions 5 - 8 in the second survey", out.width = '100%'}
knitr::include_graphics(here("outputs/images/survey2_q5q8.png"))
```
```{r survey2q9toq12, echo=FALSE,fig.align='center',fig.cap="Survey questions 9 - 12 in the second survey", out.width = '100%'}
knitr::include_graphics(here("outputs/images/survey2_q9q12.png"))
```

```{r survey2q13toq15, echo=FALSE,fig.align='center',fig.cap="Survey questions 13 - 15 in the second survey", out.width = '60%'}
knitr::include_graphics(here("outputs/images/survey2_q13q14q15.png"))
```

```{r survey2t, echo=FALSE, fig.align='center', fig.cap="Thanks section of the second survey", out.width = '80%'}
knitr::include_graphics(here("outputs/images/survey2_thanks.png"))
```
